---
title: "Demand_prj_Sc"
author: "MHarb"
date: "20/10/2020"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

```{r}
#source 1: https://www.datanovia.com/en/lessons/transform-data-to-normal-distribution-in-r/

#Drawing the raw data
library(ggpubr)
library(moments)
library(ggplot2)

#Demo data Kaala growth
GrowthRates <- read.csv("Kaala_Data_GR.csv")
#skewness(GrowthRates$Plantation_GR, na.rm = TRUE)
#skewness(GrowthRates$Crops_GR, na.rm = TRUE)
head(GrowthRates)

#Plantation: ..... .
# Agri: .....
# Distribution of Plantation growth rate variable
ggdensity(GrowthRates, x = "Plantation_GR", fill = "lightgray", title = "Plantation") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")

# Distribution of crops growth rate variable
ggdensity(GrowthRates, x = "Crops_GR", fill = "lightgray", title = "crops") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")

# Distribution of Rainfed growth rate variable
ggdensity(GrowthRates, x = "Rainfed_GR", fill = "lightgray", title = "Rainfed") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
# Distribution of Irrigated growth rate variable
ggdensity(GrowthRates, x = "Irrigated_GR", fill = "lightgray", title = "Irrigated") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
# Distribution of Total_Agri variable
ggdensity(GrowthRates, x = "Total_GR", fill = "lightgray", title = "Total_Agri") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
```
```{r}
#Transforming to normal
#Source:https://rdrr.io/cran/Johnson/man/Johnson-package.html
##Johnson Transformation
library(Johnson)

rawdata <- read.csv("Kaala_Data_GR.csv")

x1 <- rawdata$Rainfed_GR
x2 <- rawdata$Irrigated_GR
x3 <- rawdata$Crops_GR
x4 <- rawdata$Plantation_GR
x5 <- rawdata$Total_GR

y1=RE.Johnson(x1)
z1 <- RE.Johnson(y1$transformed)
#skewness(z1$transformed, na.rm = TRUE)

y2=RE.Johnson(x2)
z2 <- RE.Johnson(y2$transformed)

y3=RE.Johnson(x3)
z3 <- RE.Johnson(y3$transformed)

y4=RE.Johnson(x4)
z4 <- RE.Johnson(y4$transformed)

y5=RE.Johnson(x5)
z5 <- RE.Johnson(y5$transformed)

dfrm <- data.frame(z1,z2,z3,z4,z5)
write.csv(dfrm,'normal_trans02.csv')
```

```{r}
#3.checking normality after the tranformation
#Drawing the raw data
library(ggpubr)
library(moments)
library(ggplot2)

#Demo data Kaala growth
GrowthRates <- read.csv("normal_trans02.csv")
head(GrowthRates)

# Distribution of Plantation growth rate variable
ggdensity(GrowthRates, x = "transformed", fill = "lightgray", title = "Plantation") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")

# Distribution of crops growth rate variable
ggdensity(GrowthRates, x = "transformed.1", fill = "lightgray", title = "crops") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")

# Distribution of Rainfed growth rate variable
ggdensity(GrowthRates, x = "transformed.2", fill = "lightgray", title = "Rainfed") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
# Distribution of Irrigated growth rate variable
ggdensity(GrowthRates, x = "transformed.3", fill = "lightgray", title = "Irrigated") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
# Distribution of Total_Agri variable
ggdensity(GrowthRates, x = "transformed.4", fill = "lightgray", title = "Total_Agri") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
```
```{r}
#source:https://stats.stackexchange.com/questions/43482/transformation-to-increase-kurtosis-and-skewness-of-normal-r-v
fs = function(x,epsilon,delta) dnorm(sinh(delta*asinh(x)-epsilon))*delta*cosh(delta*asinh(x)-epsilon)/sqrt(1+x^2)

vec = seq(-15,15,0.001)

plot(vec,fs(vec,0,1),type="l")
points(vec,fs(vec,1,1),type="l",col="red")
points(vec,fs(vec,2,1),type="l",col="blue")
points(vec,fs(vec,-1,1),type="l",col="red")
points(vec,fs(vec,-2,1),type="l",col="blue")

vec = seq(-5,5,0.001)

plot(vec,fs(vec,0,0.5),type="l",ylim=c(0,1))
points(vec,fs(vec,0,0.75),type="l",col="red")
points(vec,fs(vec,0,1),type="l",col="blue")
points(vec,fs(vec,0,1.25),type="l",col="red")
points(vec,fs(vec,0,1.5),type="l",col="blue")
```

