---
title: "Demand_prj_Sc"
author: "MHarb"
date: "20/10/2020"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

```{r}
#source 1: https://www.datanovia.com/en/lessons/transform-data-to-normal-distribution-in-r/

#Drawing the raw data
library(ggpubr)
library(moments)
library(ggplot2)

#Demo data Kaala growth
GrowthRates <- read.csv("Kaala_Data_GR.csv")
#skewness(GrowthRates$Plantation_GR, na.rm = TRUE)
#skewness(GrowthRates$Crops_GR, na.rm = TRUE)
head(GrowthRates)

#Plantation: ..... .
# Agri: .....
# Distribution of Plantation growth rate variable
ggdensity(GrowthRates, x = "Plantation_GR", fill = "lightgray", title = "Plantation") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")

# Distribution of crops growth rate variable
ggdensity(GrowthRates, x = "Crops_GR", fill = "lightgray", title = "crops") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")

# Distribution of Rainfed growth rate variable
ggdensity(GrowthRates, x = "Rainfed_GR", fill = "lightgray", title = "Rainfed") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
# Distribution of Irrigated growth rate variable
ggdensity(GrowthRates, x = "Irrigated_GR", fill = "lightgray", title = "Irrigated") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
# Distribution of Total_Agri variable
ggdensity(GrowthRates, x = "Total_GR", fill = "lightgray", title = "Total_Agri") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
```
```{r}
#Transforming to normal
#Source:https://rdrr.io/cran/Johnson/man/Johnson-package.html
##Johnson Transformation
library(Johnson)

rawdata <- read.csv("Kaala_Data_GR.csv")

x1 <- rawdata$Rainfed_GR
x2 <- rawdata$Irrigated_GR
x3 <- rawdata$Crops_GR
x4 <- rawdata$Plantation_GR
x5 <- rawdata$Total_GR

y1=RE.Johnson(x1)
z1 <- RE.Johnson(y1$transformed)
#skewness(z1$transformed, na.rm = TRUE)

y2=RE.Johnson(x2)
z2 <- RE.Johnson(y2$transformed)

y3=RE.Johnson(x3)
z3 <- RE.Johnson(y3$transformed)

y4=RE.Johnson(x4)
z4 <- RE.Johnson(y4$transformed)

y5=RE.Johnson(x5)
z5 <- RE.Johnson(y5$transformed)

dfrm <- data.frame(z1,z2,z3,z4,z5)
write.csv(dfrm,'normal_trans02.csv')
```

```{r}
#3.checking normality after the tranformation
#Drawing the raw data
library(ggpubr)
library(moments)
library(ggplot2)

#Demo data Kaala growth
GrowthRates <- read.csv("normal_trans02.csv")
head(GrowthRates)

# Distribution of Plantation growth rate variable
ggdensity(GrowthRates, x = "transformed", fill = "lightgray", title = "Plantation") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")

# Distribution of crops growth rate variable
ggdensity(GrowthRates, x = "transformed.1", fill = "lightgray", title = "crops") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")

# Distribution of Rainfed growth rate variable
ggdensity(GrowthRates, x = "transformed.2", fill = "lightgray", title = "Rainfed") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
# Distribution of Irrigated growth rate variable
ggdensity(GrowthRates, x = "transformed.3", fill = "lightgray", title = "Irrigated") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
# Distribution of Total_Agri variable
ggdensity(GrowthRates, x = "transformed.4", fill = "lightgray", title = "Total_Agri") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
```
```{r}
#The extrapolation code is working perfect
 library(forecast)
h <- 10
x <- read.csv("transformed.csv")
marathon <- ts(x[,2:length(x)], start = 2004, end = 2018)
fit.lin <- tslm(marathon ~ trend)
fcasts.lin <- forecast(fit.lin, h = h)
fit.exp <- tslm(marathon ~ trend, lambda = 0)

fcasts.exp <- forecast(fit.exp, h = h)

t <- time(marathon)
t.break1 <- 2030
t.break2 <- 2040
tb1 <- ts(pmax(0, t - t.break1), start = 2004)
tb2 <- ts(pmax(0, t - t.break2), start = 2004)

fit.pw <- tslm(marathon ~ t + tb1 + tb2)
t.new <- t[length(t)] + seq(h)
tb1.new <- tb1[length(tb1)] + seq(h)
tb2.new <- tb2[length(tb2)] + seq(h)

newdata <- cbind(t=t.new, tb1=tb1.new, tb2=tb2.new) %>%
  as.data.frame()
fcasts.pw <- forecast(fit.pw, newdata = newdata)

fit.spline <- tslm(marathon ~ t + I(t^2) + I(t^3) +
  I(tb1^3) + I(tb2^3))
fcasts.spl <- forecast(fit.spline, newdata = newdata)

autoplot(marathon) +
  autolayer(fitted(fit.lin), series = "Linear") +
  autolayer(fitted(fit.exp), series = "Exponential") +
  autolayer(fitted(fit.pw), series = "Piecewise") +
  autolayer(fitted(fit.spline), series = "Cubic Spline") +
  autolayer(fcasts.pw, series="Piecewise") +
  autolayer(fcasts.lin, series="Linear", PI=FALSE) +
  autolayer(fcasts.exp, series="Exponential", PI=FALSE) +
  autolayer(fcasts.spl, series="Cubic Spline", PI=FALSE) +
  xlab("Year") + ylab("LC Growth rate") +
  ggtitle("Growth Demand") +
  guides(colour = guide_legend(title = " "))

 

```


```{r}
#source:https://stats.stackexchange.com/questions/43482/transformation-to-increase-kurtosis-and-skewness-of-normal-r-v
# the degree for the different grades of skewness is working perfectly
fs = function(x,epsilon,delta) dnorm(sinh(delta*asinh(x)-epsilon))*delta*cosh(delta*asinh(x)-epsilon)/sqrt(1+x^2)

GrowthRates <- read.csv("normal_trans02.csv")
GR = seq(-4,4,0.0001)#GrowthRates$transformed#

plot(GR,fs(GR,0,1), 
     type="l",     
    lty=1,              # Line type: 0=blank, 1=solid, 2=dashed, 3=dotted, 4=dotdash, 5=longdash, 6=twodash  
     ,col="black")
points(vec,fs(vec,1,1),type="l",lty=2,col="green")
points(vec,fs(vec,2,1),type="l",lty=2,col="blue")
points(vec,fs(vec,-1,1),type="l",lty=2,col="brown")
points(vec,fs(vec,-2,1),type="l",lty=2,col="red")

# GR = seq(-0,2,0.001)#GrowthRates$transformed#
# 
# plot(vec,fs(vec,0,0.5),type="l",ylim=c(0,1))
# points(vec,fs(vec,0,0.75),type="l",col="red")
# points(vec,fs(vec,0,1),type="l",col="blue")
# points(vec,fs(vec,0,1.25),type="l",col="red")
# points(vec,fs(vec,0,1.5),type="l",col="blue")
```



```{r}
#Source:https://stackoverflow.com/questions/56313594/reverse-johnson-transformation
# This transformation to normal and inverting it is working perfectly
library(bestNormalize)

mydata <- read.csv("Kaala_Data_GR.csv")

mydata$Rainfed_GR
skewness(mydata$Rainfed_GR, na.rm = TRUE)

# Store the transformation object
yj_obj <- yeojohnson(mydata$Rainfed_GR,standardize=TRUE)
yj_obj

# # Perform transformation
 yj_vals <- predict(yj_obj)
yj_vals
skewness(yj_vals, na.rm = TRUE)

# 
# # Reverse transformation
 orig_vals <- predict(yj_obj, newdata = yj_vals, inverse = TRUE)
orig_vals
# 
# # Should be the same as the original values
 all.equal(orig_vals, mydata$new)
 
 #print(Back_2_Orig)
#write.csv(c(mydata$Rainfed_GR,yj_vals),'Back_2_Orig.csv')

```

